---
title: "Reverse Engineering Project"
author: "Student names here"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false \
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Turn off scientific notation
options(scipen=999)
```

## Introduction

In this notebook, we are reverse engineering the story, [STORY NAME](STORY%20URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data

without_parole <- read_csv('data/louisiana_life_without_parole_sept_2021.csv')
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 
without_parole <- read_csv('data/lousiana_life_without_parole_sept_2021.csv') |> clean_names()

```

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: [The men and women are serving life sentences in the state.]
-   **Analysis summary**: We are first counting the over 4,000 Louisiana citizens that are in the spreadsheet.

```{r}
# Put code to reverse engineer sentence here

without_parole |>
  group_by('DOC Number') |>
  summarize(count=n())
  

# Display results of code below this codeblock

```

### Sentence 2

-   **Sentence text**: "More than half of the people serving life is Lousiana were convicted of second-degree murder, our investigation found.
-   **Analysis summary**: I didn't get the answer, having some errors.

```{r}
# Put code to reverse engineer sentence here

without_parole |>
  filter(offense= 'Second Degree Murder') |> 
  group_by('DOC NUMBER') |>
  summarize(count=n(0.5))

# Display results of code below this codeblock

```

### Sentence 3

-   **Sentence text**: ...Including over three-quarters of the 124 women serving life (this is part of a sentence talking about people convicted of second-degree murder)
-   **Analysis summary**: Three-quarters of the 124 women would total 96.

```{r}
# Put code to reverse engineer sentence here

parole |>
  filter(gender) |>
  summarize(count=n(96))


# Display results of code below this codeblock

```

### Sentence 4

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
