---
title: "Data "
author: "Marwa Barakat, Benji Ferraro"
date: "4/23/2024"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false \
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Turn off scientific notation
options(scipen=999)
```

## Introduction

In this notebook, we are reverse engineering the story, [STORY NAME](STORY%20URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data


# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

board_game_data <- read_csv2("archive/bgg_dataset.csv") |>

# Clean required data and prepare for analysis if needed

clean_names()

```

There are 20,343 rows and 14 total columns. There seem to be some current limitations and flaws after cleaning the data. For example , on the minimum players and year-published columns there are negative numbers or zero values, indicating a possible error in the data set as that shouldn't be possible. Limits that we found initially could be there are only board games included that were manufactured before 2023. Maybe for some of the board games with an incorrect year manufacturing date or minimum player suggestion we can verify on Amazon, the retailer or Google as extra research. Possibly researching the brands and companies behind the board games would be a piece of extra beneficial data as it is not included in our current spreadsheet. The complexity average column we are pretty sure means how difficult a game is especially for younger players, but finding more concrete confirmation of what that column represents could be helpful.

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: Compare the average rating across all board games between 1900 and 2000, and 2000-2022.
-   **Analysis summary**:

```{r}
# Put code to reverse engineer sentence here

board_games |>
  group_by(rating_average) |>
  
  start_date <- as.Date("1900/01/01") |>

  end_date <- as.Date("2023/01/01") |>
  

# Display results of code below this codeblock

```

### Sentence 2

-   **Sentence text**:
-   **Analysis summary**:

```{r}
# Put code to reverse engineer sentence here

# This code shows the number of reviews for games that are considered multiplayer (2 or more players) compared to those that are considered singleplayer (no more than 1 player)

game_reviews <- game_reviews |>
  #Code for singleplayer or multiplayer
  mutate(
   player_type = case_when(
    max_players <= 1~ "Singleplayer",
    max_players >= 2 ~ "Multiplayer",
        .default = NA
      )
  )
#Group by player type and count the number of ratings. Also, a sum of the number of games considered multiplayer and singleplayer for context.
game_reviews |> group_by(player_type)|>
  summarise("# of Ratings" = sum(users_rated), "# of Games" = n())

# Display results of code below this codeblock

```

### Sentence 3

-   **Sentence text**:
-   **Analysis summary**:

```{r}
# Put code to reverse engineer sentence here




# Display results of code below this codeblock

```

### Sentence 4

-   **Sentence text**:
-   **Analysis summary**:

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**:
-   **Analysis summary**:

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```
