---
title: "Data "
author: "Marwa Barakat, Benji Ferraro"
date: "4/23/2024"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false \
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Turn off scientific notation
options(scipen=999)
```

## Introduction

In this notebook, we are reverse engineering the story, [STORY NAME](STORY%20URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data


# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

board_game_data <- read_csv2("archive/bgg_dataset.csv") |>

# Clean required data and prepare for analysis if needed

clean_names()

```

There are 20,343 rows and 14 total columns. There seem to be some current limitations and flaws after cleaning the data. For example , on the minimum players and year-published columns there are negative numbers or zero values, indicating a possible error in the data set as that shouldn't be possible. Limits that we found initially could be there are only board games included that were manufactured before 2023. Maybe for some of the board games with an incorrect year manufacturing date or minimum player suggestion we can verify on Amazon, the retailer or Google as extra research. Possibly researching the brands and companies behind the board games would be a piece of extra beneficial data as it is not included in our current spreadsheet. The complexity average column we are pretty sure means how difficult a game is especially for younger players, but finding more concrete confirmation of what that column represents could be helpful.

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: [The men and women are serving life sentences in the state.]
-   **Analysis summary**: We are first counting the over 4,000 Louisiana citizens that are in the spreadsheet.

```{r}
# Put code to reverse engineer sentence here


  

# Display results of code below this codeblock

```

### Sentence 2

-   **Sentence text**: "More than half of the people serving life is Lousiana were convicted of second-degree murder, our investigation found.
-   **Analysis summary**: I didn't get the answer, having some errors.

```{r}
# Put code to reverse engineer sentence here

without_parole |>
  filter(offense= 'Second Degree Murder') |> 
  group_by('DOC NUMBER') |>
  summarize(count=n(0.5))

# Display results of code below this codeblock

```

### Sentence 3

-   **Sentence text**: ...Including over three-quarters of the 124 women serving life (this is part of a sentence talking about people convicted of second-degree murder)
-   **Analysis summary**: Three-quarters of the 124 women would total 96.

```{r}
# Put code to reverse engineer sentence here

parole |>
  filter(gender) |>
  summarize(count=n(96))


# Display results of code below this codeblock

```

### Sentence 4

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
